Singapore's Public Housing Affordability

### 2023-11-23 about.qmd
Weekly Update

---
title: "Data Story"
---

<br>

### Investigating Singapore's Resale Flat Prices from 1990 to 2023

##### Is public housing in Singapore affordable for the average Singaporean?

<br> This is where my introduction will be. This is just a placeholder for potential data sets!

```{r, eval=TRUE,echo=FALSE}
library(tidyverse)
starwars
```

>>>>

---
title: "My Experiences"
---

![](src/images/aboutme.png)

## Education
**National University of Singapore**\
*Bachelor of Social Sciences [Hons.], Communications New Media / Sociology, Social Sciences*
<br> Aug 2022 - Present

**Temasek Polytechnic**\
*Diploma with Merit, Business Information Technology*
<br> Apr 2018 - Apr 2021

**ITE College Central**\
*Higher Nitec in Business Event Management*
<br> Apr 2013 - Apr 2015

## Work and Internship Experience - [My LinkedIn Profile](https://www.linkedin.com/in/marzuki-nooranas-b5947b17a/)

**Product Specialist**\
*Apple South Asia* <br> Aug 2023 - Present · 4 mos

**Galaxy Specialist · Part-time**\
*Samsung Electronics Singapore* <br>Feb 2018 - Jan 2023 · 5 yrs

**Business Information Technology Interest Group - Honorary Secretary**\
*Temasek Polytechnic* <br>Apr 2019 - Apr 2021 · 2 yrs 1 mo

**Application Development Intern**\
*Accenture · Internship* <br>Apr 2020 - Aug 2020 · 5 mos

**Marketing Research Intern**\
*Shopee Jakarta, Indonesia· Internship* <br>Mar 2020 - Apr 2020 · 2 mos

**Instructor**\
*Singapore Civil Defence Force · Full-time* <br>Feb 2016 - Nov 2017 · 1 yr 10 mos

**Attraction Host Lead**\
*Sentosa Development Corporation · Part-time* <br>Oct 2013 - Nov 2015 · 2 yrs 2 mos

### 2023-11-23 datastory.qmd
Weekly Update

https://ycharts.com/indicators/5year_5year_forward_inflation_expectation_rate#:~:text=Basic%20Info,long%20term%20average%20of%202.25%25.

https://www.dbs.com.sg/personal/articles/nav/my-home/all-about-home-loans#:~:text=With%20HDB%20loans%2C%20the%20interest,has%20not%20changed%20in%20years.

>>>>

https://ycharts.com/indicators/5year_5year_forward_inflation_expectation_rate#:\~:text=Basic%20Info,long%20term%20average%20of%202.25%25.

https://www.dbs.com.sg/personal/articles/nav/my-home/all-about-home-loans#:\~:text=With%20HDB%20loans%2C%20the%20interest,has%20not%20changed%20in%20years.
